---
title: "Presentación Análisis Exploratorio y Estadístico de datos"
subtitle: 'Mortalidad de *Salmo salar* por causa de bloom de algas y oxígeno disuelto para un barrio del sur de Chile'
author: "Felipe Tucca"
institute: Instituto Tecnológico del Salmón (INTESAL)
date: '2022-06-29'
output: beamer_presentation
  theme: "CambridgeUS"
    colortheme: "dolphin"
      fonttheme: "professionalfonts"
      includes:
        in_header: mystyle.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

